### 2025-02-18 analysis/analysis.qmd
feat(analysis): update analysis based on main branch file
- simplify splits - update feature_n_complexity

```{r,results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_categories,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(S)

@@

```{r, results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # removemissing values

S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))

m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity_genre,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
```

@@

```{r,results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove 
S <- summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_categories,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_categories),n=n(),obs=sum(stimulus_n))
print(S)

@@

```{r, results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp<-tmp[!is.na(tmp$feature_n_categories),] # remove missing values

S<-summarise(group_by(tmp,feature_n_complexity_genre),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))

m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity_genre,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
```

@@

```{r}
m.cor_complexity <- update(m.cor.c, 
       subgroup = C_summary$feature_n_complexity_genre, 
       tau.common = FALSE,
       prediction = TRUE)

print(m.cor_complexity)
```
### By model type

>>>>

```{r,results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove 
S <- summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
print(S)

@@

```{r, results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="valence")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # removemissing values

S<-summarise(group_by(tmp,stimulus_genre_mixed),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))

m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  stimulus_genre_mixed,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
```

@@

```{r,results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove 
S <- summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))
```

```{r}
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values
m.cor3 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  feature_n_complexity,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor3)
S<-summarise(group_by(tmp,feature_n_complexity),n=n(),obs=sum(stimulus_n))
print(S)

@@

```{r, results='asis'}
tmp <- dplyr::filter(R_summary,dimension=="arousal")
tmp<-tmp[!is.na(tmp$feature_n_complexity),] # remove missing values

S<-summarise(group_by(tmp,stimulus_genre_mixed),n=n(),obs=sum(stimulus_n))
print(knitr::kable(S))

m.cor4 <- metacor(cor = valuesMax,     # values 
                 n = stimulus_n,
                 studlab = citekey, # unique_id
                 data = tmp,
                 common = FALSE,
                 random = TRUE,
                 prediction = TRUE,
                 subgroup =  stimulus_genre_mixed,
#                 backtransf = TRUE,
#                 sm = "ZCOR",
                 method.tau = "REML",# could be PM (Paule-Mandel) as well
                 method.random.ci = "HK", 
                 title = "MER: Regression: Valence: Summary")
print(m.cor4)
```

@@

```{r}
# m.cor_complexity <- update(m.cor.c, 
#        subgroup = C_summary$feature_n_complexity_genre, 
#        tau.common = FALSE,
#        prediction = TRUE)
# 
# print(m.cor_complexity)
```
### By model type
